Probability

### 2016-04-20 prob.tex
prob.tex "\subsection{Quantum Probability Spaces}" Add a proof...

\amr{CHECK because sum of
    projections may not be a projection}
\end{itemize}

\yutsung{The following is the diagram for quantum probability objects
and their corresponding physical meaning (in parentheses):
\[
\xymatrix{\textrm{projections (\textrm{events})}\ar[d]^{\mu_{\psi}\textrm{(probability)}} & \subsetneq & \textrm{Hermitian operators (observables)}\ar[d]^{\mu_{\psi}\textrm{(expectation value)}} & \subsetneq & \textrm{all operators in a }*\textrm{-algebra(?)}\ar[d]^{\mu_{\psi}\textrm{(?)}}\\
\left[0,1\right] & \subsetneq & \mathbb{R} & \subsetneq & \mathbb{C}
}
\]
Although the above paragraph claimed $\qevents$ is a set of events,
``all linear combinations of \emph{projections}'' and $\left\{ \sum_{j=1}^{k}\lambda_{j}P_{j}~\middle|~\lambda_{1},\ldots,\lambda_{k}\in\mathbb{C}\right\} $
gives all operators in a $*$-algebra. Therefore, I got confused you
want $\qevents$ be ``the set of all events'' or ``the set of all
operators in a $*$-algebra''...}

>>>>

\amr{CHECK because sum of
    projections may not be a projection}

\yutsung{I am going to verify if $\proj{\psi_{1}}+\proj{\psi_{2}}$
is a projection, then they are orthogonal. Given any state $\ket{\phi}=a\ket{\psi_{1}}+b\ket{\psi_{2}}$,
if $\proj{\psi_{1}}+\proj{\psi_{2}}$ is a projection, then 
\begin{eqnarray*}
\ket{\phi} & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\ket{\phi}\\
 & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\left(a\ket{\psi_{1}}+b\ket{\psi_{2}}\right)\\
 & = & a\ket{\psi_{1}}+b\ket{\psi_{2}}+a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
\end{eqnarray*}
Therefore, we have 
\begin{eqnarray*}
0 & = & a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
\end{eqnarray*}
However, $a$ and $b$ can be any numbers. Therefore, we must have
$0=\ip{\psi_{2}}{\psi_{1}}=\ip{\psi_{1}}{\psi_{2}}$.}
\end{itemize}
\yutsung{The following is the diagram for quantum probability objects
and their corresponding physical meaning (in parentheses): 
\[
\xymatrix{\textrm{projections (events)}\ar[d]^{\mu_{\psi}\textrm{(probability)}} & \subsetneq & \textrm{Hermitian operators (observables)}\ar[d]^{\mu_{\psi}\textrm{(expectation value)}} & \subsetneq & \textrm{all operators in a }*\textrm{-algebra(?)}\ar[d]^{\mu_{\psi}\textrm{(?)}}\\
\left[0,1\right] & \subsetneq & \mathbb{R} & \subsetneq & \mathbb{C}
}
\]
}
